Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Explain no_long_message

\subsubsection{no_long_message}
\label{subs:no_long_message}

>>>>

\subsubsection{no_long_message}
\label{subs:no_long_message}
The subject line should be limited to less than 10 words. This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words. The reasoning behind this criterion again is, that many words hint at more than one logical changeset in one commit. Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less time. If there is need for longer explanations, the body should be used.
